---
title: "ST 511 Project"
author: "Haotian Jia"
date: "Winter 2021"
output:
  pdf_document: default
  word_document: default
#subtitle: Due on March 12, 2021
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction
```{r include=FALSE}
# Load libraries we need
library(ggplot2)
```

In this final project, I found the data set from the $Kaggle.com$, and the name of the data set is "Medical Cost Personal Datasets". Therefore, the prposal of this experiment is to test whether BMI _(Body mass index, Ideally 18.5 to 24.9)_ and insurance charges are related to different regions.

The red box plot shown below is the relationship between BMI and region. In addition, the yellow box plot shown below is the relationship between BMI and region.


```{r echo=FALSE}
# Read the data from file
scores <- read.csv("D:\\insurance.csv")
# Draw box diagram
ggplot(data = scores, aes(region, bmi))+
  geom_boxplot(fill = "red")
```
```{r echo=FALSE}
ggplot(data = scores, aes(region, charges))+
  geom_boxplot(fill = "yellow")
```

## Methods

Since I want to test whether BMI _(Body mass index)_ and insurance charges are related to different regions, so I prefer to use $ANOVA$ to test the data because of multiple samples. Therefore, I made the following settings:
- The Null hypothesis is $H_0 : \mu_1=\mu_2=\mu_3=\mu_4$;
- The alternative hypothesis is $H_A :$ At least two population means are different;
- $\alpha=0.05$.


## Results



```{r echo=FALSE}
anova(lm(bmi ~ region, data = scores))
```
```{r echo=FALSE}
anova(lm(charges ~ region, data = scores))
```
```{r echo=FALSE}
mod <- lm(bmi ~ region, data = scores)
scores$fitted <- mod$fitted
scores$resid <- mod$resid
ggplot(scores, aes(fitted,resid,color = region))+
  geom_point()
```


